D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-05 ootavacuous.tex
Move multi-cycle litmus test after three-process test
The two litmus tests are closely related, so move their sections
together.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
"Multi-Cycle Litmus Test": Reword
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

\subsection{Multi-Cycle Litmus Tests}
\label{app:Multi-Cycle Litmus Tests}

Listing~\ref{lst:Multi-Cycle Litmus Test}
shows an expansion to four threads of Causality Test Case 4, which is shown in
Listing~\ref{lst:Causality Test Case 4}
and discussed in
Appendix~\ref{app:Causality Test Case 4}.
The \co{herd7} tool shows multiple different possible OOTA cycles,
as expected.
However, the value returned by each thread's load directly affects the
value stored, so there is a semantic dependency in each thread.
Therefore, none of these OOTA cycles can happen in a compiler-based
C++ implementation.

>>>>

\subsection{Multi-Cycle Litmus Test}
\label{app:Multi-Cycle Litmus Test}

Listing~\ref{lst:Multi-Cycle Litmus Test}
expands
Listing~\ref{lst:Causality Test Case 4}
in a different way, moving to four threads but having only the
original two variables \co{x} and \co{y}.
The \co{herd7} tool shows multiple different possible OOTA cycles,
as expected.
However, the value returned by each thread's load directly affects the
value stored, so there is a semantic dependency in each thread.
Therefore, none of these OOTA cycles can arise in a compiler-based
C++ implementation.

@@
